### 2016-12-09 local-capability-machine.tex
more indentation
.
Tentative formulation of an scall lemma.
changed conclusion of scall lemma to be in terms of observation relation
scall lemma: changed confs to conform with domain
removed preview from preamble

%% make latex preview-mode work with natbib...
\usepackage[displaymath,floats,graphics,textmath,footnotes]{preview}

@@

\subsection{Lemmas}
We expect the following lemmas to hold true:
\subsubsection{Memory Segment Satisfaction}
\begin{lemma}[Downwards closure]
  \begin{align*}
    &\forall \hs, n' \leq n, W \ldotp \\
    &\quad \heapSat[\hs]{n}{W} \Rightarrow \heapSat[\hs]{n'}{W}
  \end{align*}
\end{lemma}

>>>>

%% make latex preview-mode work with natbib...
%\usepackage[displaymath,floats,graphics,textmath,footnotes]{preview}

@@

\subsection{Lemmas}

\begin{definition}
  We say that $(\ms,\reg) \text{ is looking at } [i_0,\cdots,i_n]$ if
  \begin{itemize}
  \item $\reg(\pcreg) = ((p,g),b,e,a)$
  \item $p = \rwx$, $p = \exec$, or $p = \rwlx$
  \item $a+n\leq e$, $b\leq a\leq e$
  \item $\ms(a+0,\cdots,a+n) = [i_0,\cdots,i_n]$
  \end{itemize}
\end{definition}

\begin{definition}
  $(\ms,\reg) \text{ has stack $\ms_\stk$ with $\ms_{\mathit{unused}}$ unused}$

  \begin{itemize}
  \item $\reg(r_\stk) =((\rwlx,\_),b_\stk,e_\stk,a_\stk)$
  \item $\dom(\ms_{\mathit{unused}}) = [a_\stk+1,\cdots,e_\stk]$
  \item $\dom(\ms_\stk) = [b_\stk,\cdots,a_\stk]$
  \item $b_\stk - 1\leq a_\stk$
  \end{itemize}
\end{definition}

\begin{lemma}[$\mathtt{scall}$ works]
  If
  \begin{itemize}
  \item $\heapSat[\ms]{n}{W}$ 
  \item $(\reg,\ms) \text{ is looking at } \mathtt{scall}(r(\overline{r_{\mathit{arg}}},
    \overline{r_{\mathit{priv}}}))$
  \item $(\reg,\ms) \text{ has stack $\ms_\stk$ with $\ms_{\mathit{unused}}$ unused}$
  \item[Hyp-Callee] If
    \begin{itemize}
    \item $\ms_{\mathit{unused}} = \ms_{\mathit{act}}
      \uplus \ms_{\mathit{unused}}'$
    \item $W' =
      \revokeTemp{W}[\iota^{\sta}(\temp,\ms_\stk\uplus\ms_{\mathit{act}}),\iota^{\pwl}(\dom(\ms_{\mathit{unused}}'))]$,
    \item $\memSat[n-1]{\ms''}{W'}$
    \item $(\reg',\ms'') \text{ has stack $\emptyset$ with
        $\ms_{\mathit{unused}}'$ unused}$,
    \item $\reg'= \reg_0[\pcreg\mapsto\updatePcPerm{\reg(r)},
      \overline{r_{\mathit{arg}}} \mapsto \reg(\overline{r_{\mathit{arg}}}),r_0
      \mapsto c_{\mathit{ret}}]$
    \item $(n,c_{\mathit{ret}}) \in \stdvr(W')$
    \end{itemize}
    then we have that $(\reg',\ms'') \in \observations(W')$
  \item[Hyp-Cont] ...
  \end{itemize}
  Then 
  \begin{itemize}
    \item $(\reg,\ms) \in \observations(W)$
  \end{itemize}

  Note: $k_{\mathit{act-rec}}$ is the (standard) size of an activation record (2
  words for stack pointer and return pointer and some fixed number of words for
  the standard return instructions).
\end{lemma}
\begin{proof}
  Apply Hyp-Callee with $\ms_{\mathit{act}} = ...$. 
\end{proof}

We expect the following lemmas to hold true:
\subsubsection{Memory Segment Satisfaction}
\begin{lemma}[Downwards closure]
  \begin{align*}
    &\forall \hs, n' \leq n, W \ldotp \\
    &\quad \heapSat[\hs]{n}{W} \Rightarrow \heapSat[\hs]{n'}{W}
  \end{align*}
\end{lemma}
